ME780 Assignment 1

### 2016-02-12 homework/homework_1/report.tex
Update report

\section{Derivation of the Omni-directional Robot}

@@

\newpage
\section{Applying the Derived Robot Model}
\subsection{Predefined Rotation Inputs}
Applying the following rotation inputs to the wheel for 15 seconds:

@@

\subsection{Traversing East, West, North East, South East and Inplace}

@@

\newpage
\subsection{Moving in a Circle}

@@

\newpage
\subsection{Traversing in a Spiral}

@@

\newpage
\section{Measurement Model}

@@

\newpage
\section{Defining the Extended Kalman Filter for the Omni-directional Robot}

Normally if our motion model and/or measurement model is linear we can simply 
use the Kalman Filter, however in the non-linear case we have to use the 
Extended Kalman Filter (EKF). In our case we have to linearize the non-linear 
motion model $g(x_{t-1}, u_{t})$, where:

\begin{equation}
	\dot{g}(\theta, \omega) =
	\begin{bmatrix}
		\frac{2}{3} \sin(\theta) r \omega_{1}
			- \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{2}
				- \frac{1}{3} \sin(\theta) r \omega_{2}
			+ \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{3}
				- \frac{1}{3} \sin(\theta) r \omega_{3} \\
		\frac{2}{3} \cos(\theta) r \omega_{1}
			+ \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{2}
				-\frac{1}{3} \cos(\theta)r \omega_{2}
			- \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{3}
				-\frac{1}{3} \cos(\theta) r \omega_{3} \\
		\frac{1}{3l} r \omega_{1}
			+ \frac{1}{3l} r \omega_{2}
			+ \frac{1}{3l} r \omega_{3}
	\end{bmatrix}
\end{equation}

Rewriting the above in terms of state $x_{1}, x_{2}, x_{3}$, and inputs $u_{1}, u_{2}, u_{3}$, where $S$ and $C$ short hand for $sin$ and $cos$ functions.

\begin{align*}
	& g(x_{t-1}, u_{t}) = \\
	& \begin{bmatrix}
		x_{1, t - 1} + \left(
			\dfrac{2 r u_{1, t} S(x_{3, t-1})}{3}
			- \dfrac{r u_{2, t} C(x_{3, t-1})}{\sqrt{3}}
				- \dfrac{r u_{2, t} S(x_{3, t-1})}{3}
			+ \dfrac{r u_{3, t} C(x_{3, t-1})}{\sqrt{3}} 
				- \dfrac{r u_{3, t} S(x_{3, t-1})}{3}
			\right) dt \\\
		x_{2, t - 1} + \left( 
			\dfrac{2 r u_{1, t} C(x_{3, t-1})}{3}
			+ \dfrac{r u_{2, t} S(x_{3, t-1})}{\sqrt{3}}
				-\dfrac{r u_{2, t} C(x_{3, t-1})}{3}
			- \dfrac{r u_{3, t} S(x_{3, t-1})}{\sqrt{3}}
				-\dfrac{r u_{3, t} C(x_{3, t-1})}{3} 
			\right) dt \\
		x_{3, t - 1} + (\dfrac{u_{1, t} + u_{2, t} + u_{3, t}}{3l}) r dt
	\end{bmatrix}
\end{align*}

If we linearize the above w.r.t $x_{1}, x_{2}, x_{3}$ we get:

\begin{align}
	% w.r.t x_1
	\frac{\delta{g}}{\delta{x_{1}}} &=
	\begin{bmatrix}
			1 \\ 
			0 \\ 
			0
	\end{bmatrix} \\
	% w.r.t x_2
	\frac{\delta{g}}{\delta{x_{2}}} &=
		\begin{bmatrix} 
			0 \\ 
			1 \\ 
			0
		\end{bmatrix} \\
	% w.r.t x_3
	\frac{\delta{g}}{\delta{x_{3}}} &=
	\begin{bmatrix}
			0 \\ 
			0 \\ 
			1
	\end{bmatrix} \\
	% putting it back together
%	\frac{\delta{g}}{\delta{x}} &=
%		\begin{bmatrix}
%			
%		\end{bmatrix} \\
\end{align}

As for the measurement model, because it is linear we do not need to linearize 
it.

@@

>>>>

\section{Derivation of the Omni-directional Robot}
\label{sec:motion_model_derivation}

@@

\newpage
\section{Applying the Derived Robot Model}
\label{sec:applying_motion_model}

\subsection{Predefined Rotation Inputs}
\label{subsec:traverse_inputs}
Applying the following rotation inputs to the wheel for 15 seconds:

@@

\subsection{Traversing East, West, North East, South East and Inplace}
\label{subsec:traverse_directions}

@@

\newpage
\subsection{Moving in a Circle}
\label{subsec:traverse_circle}

@@

\newpage
\subsection{Traversing in a Spiral}
\label{subsec:traverse_spiral}

@@

\newpage
\section{Measurement Model}
\label{sec:measurement_model}

@@

\newpage
\section{Defining the Extended Kalman Filter for the Omni-directional Robot}
\label{sec:ekf_defintion}

The Extended Kalman filter (EKF) has two stages, the prediction and measurement 
updates. To complete the EKF we need to linearize the motion and measurement 
model, we detail that in the following sections.

\subsection{Linearizing the Motion Model}
\label{subsec:ekf_motion_model_linearization}
Normally if our motion model and/or measurement model is linear we can simply 
use the Kalman Filter, however in the non-linear case we have to use the 
Extended Kalman Filter (EKF). In our case we have to linearize the non-linear 
motion model $g(x_{t-1}, u_{t})$ using 1st order Taylor Series Expansion:

\begin{align}
	g(x_{t-1}, u_{t}) 
	& \approx 	
		g(\mu_{t - 1}, u_{t}) 
			+ \dfrac{\partial g(x_{t-1}, u_{t})}{x_{t - 1}} 
				\bigg|_{x_{t - 1} = \mu_{t - 1}}
			(x_{t - 1} - \mu_{t - 1}) \\
	& = g(\mu_{t - 1}, u_{t}) + G_{t} \cdot (x_{t - 1} - \mu_{t - 1})
\end{align}

Where $G_{t}$ is the first order differential of the non-linear motion model. 
We have, however, omitted the differentiation because we already know what 
$G_{t}$ is, since we have already derived the differential of $g(x_{t-1}, 
u_{t})$ in Section~\ref{sec:motion_model_derivation}.

\begin{equation}
	G_{t} = \dot{g}(\theta, \omega) = R(\theta)^{-1} J_{1}^{-1} J_{2} \omega
\end{equation}

Where $R(\theta)$, $J_{1}$, $J_{2}$ and $\omega$ are (derived in 
Section~\ref{sec:motion_model_derivation}):

\begin{align}
	R(\theta) &= 
 	\begin{bmatrix}
	    \cos{(\theta)} & -\sin{(\theta)} & 0 \\
	    \sin{(\theta)} & \cos{(\theta)} & 0 \\
	    0 & 0 & 1
    \end{bmatrix} \\
	J_{1} &= 
	\begin{bmatrix}
			0 & 1 & l \\
  	    	-\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l \\
   	    	\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l
    \end{bmatrix} \\
    J_{2} &=
    \begin{bmatrix}
        r & 0 & 0 \\
        0 & r & 0 \\
        0 & 0 & r
    \end{bmatrix} \\
    \omega &= 
	    \begin{bmatrix}
	       \omega_{1} \\
	       \omega_{2} \\
	       \omega_{3} \\
	    \end{bmatrix}
\end{align}

\begin{equation}
	G_{t} = \dot{g}(\theta, \omega) =
	\begin{bmatrix}
		\frac{2}{3} \sin(\theta) r \omega_{1}
			- \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{2}
				- \frac{1}{3} \sin(\theta) r \omega_{2}
			+ \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{3}
				- \frac{1}{3} \sin(\theta) r \omega_{3} \\ \\
		\frac{2}{3} \cos(\theta) r \omega_{1}
			+ \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{2}
				-\frac{1}{3} \cos(\theta)r \omega_{2}
			- \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{3}
				-\frac{1}{3} \cos(\theta) r \omega_{3} \\ \\
		\frac{1}{3l} r \omega_{1}
			+ \frac{1}{3l} r \omega_{2}
			+ \frac{1}{3l} r \omega_{3}
	\end{bmatrix}
\end{equation}

\newpage
\subsection{Linearizing the Measurement Model}
\label{subsec:ekf_measurement_model_linearization}

As for the measurement model, it does not require linearization since in 
Section~\ref{sec:measurement_model} we derived a linear measurement model. 
Therefore $H_{t} = C_{t}$.

\begin{equation}
	H_{t} = C_{t} = 
	\begin{bmatrix}
		1 & 0 & 0 \\
		0 & 1 & 0 \\
		0 & 0 & 1
	\end{bmatrix}
\end{equation}

\subsection{Summary}
\label{subsec:ekf_def_summary}

Now that we have defined what $g(x_{t - 1})$, $G_{t}$ and $H_{t}$ (along with
 intial values for the states) we have enough information to incorporate them
  into the EKF model.

@@

In the EKF we have used the following values:

\begin{align*}
	\mu_{0} &= 
		\begin{bmatrix}
			0 \\
			0 \\
			0
		\end{bmatrix} \\
	u_{0} &= 
	\begin{bmatrix}
		-15.5 \\
		-10.5 \\
		1.5
	\end{bmatrix} \\
	H_{t} &=
	\begin{bmatrix}
		1 & 0 & 0 \\
		0 & 1 & 0 \\
		0 & 0 & 1
	\end{bmatrix} \\
	G_{t} &= \dot{g}(\theta, \omega) \\
		&= R(\theta)^{-1} J_{1}^{-1} J_{2} \omega
	    \begin{bmatrix}
	        \dot{x} \\
	        \dot{y} \\
	        \dot{\theta}
	    \end{bmatrix} \\
	    &= 
	        \begin{bmatrix}
		        \cos{(\theta)} & -\sin{(\theta)} & 0 \\
		        \sin{(\theta)} & \cos{(\theta)} & 0 \\
		        0 & 0 & 1
	        \end{bmatrix}^{-1}
	        \begin{bmatrix}
	            0 & 1 & l \\
	          	-\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l \\
	        	\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l
	        \end{bmatrix}^{-1}
	        \begin{bmatrix}
	            r & 0 & 0 \\
	            0 & r & 0 \\
	            0 & 0 & r
	        \end{bmatrix}
		    \begin{bmatrix}
		       \omega_{1} \\
		       \omega_{2} \\
		       \omega_{3} \\
		    \end{bmatrix} \\
\end{align*}
